\clearpage
\addcontentsline{toc}{chapter}{Bibliografía}

\begin{thebibliography}{99}
	\bibitem{Bishop} Bishop C.M., ``Pattern recognition and machine learning". Singapur, Springer, 676 p, ISBN-10: 0-387-31073-8.
	\bibitem{Ch05} W. Chu and S.S. Keerthi, ``New Approaches to Support Vector Ordinal Regression". Proc. 22nd Int. Conf. Machine Learning (ICML ’05), pp. 145-152, 2005.
	\bibitem{Lin07} L. Lin and H.-T. Lin, ``Ordinal Regression by Extended Binary Classification". Advances in Neural Infor. Processing Systems, vol. 19, pp. 865-872, MIT Press, 2007.
	\bibitem{Mcc80} McCullagh, ``P. Regression models for ordinal data". Journal of the Royal Statistical Society, Series B (Methodological), 42, 109–142, 1980.
	\bibitem{Sh03} Shashua and A. Levin, ``Ranking with Large Margin Principle: Two Approaches", Advances in Neural Inform. Processing Systems, vol. 15, 961-968, MIT Press, 2003.
	\bibitem{RPROP} Riedmiller, Martin. ``RPROP - Descriptión and Implmentation Details". University of Karlsruhe. Technical Report, 1994.
	\bibitem{iRPROP+} Igel, Christian; Hüsken, Michael. ``Empirical evaluation of the improved RPROP learning algorithms". Institut für Neuroinformatik, Ruhr-Universität Bochum. Germany, 2001.
	\bibitem{Matlab} ``MATLAB version 2010a for Ubuntu". Natick, Massachusetts. The MathWorks Inc., 2010.
	\bibitem{Matlab_ref} ``Documentación oficial de MATLAB". Natick, Massachusetts. The MathWorks Inc., 2010. Enlace: \url{http://www.mathworks.com/help/techdoc/}
	\bibitem{Matlab_nnet} ``Documentación oficial de MATLAB para el Toolbox NNET". Natick, Massachusetts. The MathWorks Inc., 2010. Enlace: \url{http://www.mathworks.com/help/toolbox/nnet/}
	\bibitem{Matlab_gui} ``Documentación oficial de MATLAB para creación de GUIs (Graphical User Interfaces)". Natick, Massachusetts. The MathWorks Inc., 2010. Enlace: \url{http://www.mathworks.com/help/techdoc/creating_guis/bqz79mu.html}
	\bibitem{UML} G. Booch, J. Rumbaugh, I. Jacobson, ``El lenguaje Unificado de Modelado". Ed. Addison Wesley Iberoamericana. Madrid, 1999.
\end{thebibliography}